Packaging research artefacts with RO-Crate

### 2022-01-02 latex/ro-crate.tex
final bibliography fixes

%b42 ###bbsrt2
%b30 ###
\bibitem{doi:10.17487/rfc3987}
%
\begin{botherref}
\oauthor{\binits{M.}~\bsnm{Duerst}} and
\oauthor{\binits{M.}~\bsnm{Suignard}},
Internationalized resource identifiers ({IRI}s),
RFC 3987,
\bsertitle{Internet Requests for Comments},
\bpublisher{RFC Editor},
\byear(2005).
\bid{doi={10.17487/rfc3987}}
\end{botherref}
%
\OrigBibText
M.~Duerst and
M.~Suignard,
Internationalized resource identifiers ({IRI}s),
RFC 3987,
2005.
doi:10.17487/rfc3987.
\url{https://www.rfc-editor.org/info/rfc3987}.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b74 ###bbsrt2
%b26 ###
\bibitem{doi:10.17487/rfc8493}
%
\begin{botherref}
\oauthor{\binits{J.}~\bsnm{Kunze}},
\oauthor{\binits{J.}~\bsnm{Littman}},
\oauthor{\binits{E.}~\bsnm{Madden}},
\oauthor{\binits{J.}~\bsnm{Scancella}} and
\oauthor{\binits{C.}~\bsnm{Adams}},
The {BagIt} File Packaging Format,
(V1.0), 
RFC 8493,
\bsertitle{Internet Requests for Comments},
\bpublisher{RFC Editor},
(\byear{2018}).
\bid{doi={10.17487/RFC8493}}
\end{botherref}
%
\OrigBibText
J.~Kunze,
J.~Littman,
E.~Madden,
J.~Scancella and
C.~Adams,
The {BagIt} File Packaging Format (V1.0),
Technical Report,
2018.
doi:10.17487/RFC8493.
\url{https://www.rfc-editor.org/info/rfc8493}.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b81 ###bbsrt2
%b102 ###
\bibitem{PROVO}
%
\begin{botherref}
\oauthor{\binits{T.}~\bsnm{Lebo}},
\oauthor{\binits{S.}~\bsnm{Sahoo}},
\oauthor{\binits{D.}~\bsnm{McGuinness}},
\oauthor{\binits{K.}~\bsnm{Belhajjame}},
\oauthor{\binits{J.}~\bsnm{Cheney}},
\oauthor{\binits{D.}~\bsnm{Corsar}},
\oauthor{\binits{D.}~\bsnm{Garijo}},
\oauthor{\binits{S.}~\bsnm{Soiland-Reyes}},
\oauthor{\binits{S.}~\bsnm{Zednik}} and
\oauthor{\binits{J.}~\bsnm{Zhao}},
PROV-O: The PROV Ontology,
W3C Recommendation 30,
2013.
\url{http://www.w3.org/TR/2013/REC-prov-o-20130430/}.
\end{botherref}
%
\OrigBibText
T.~Lebo,
S.~Sahoo,
D.~McGuinness,
K.~Belhajjame,
J.~Cheney,
D.~Corsar,
D.~Garijo,
S.~Soiland-Reyes,
S.~Zednik and
J.~Zhao,
PROV-O: The PROV Ontology,
2013,
W3C Recommendation 30 April 2013.
\url{http://www.w3.org/TR/2013/REC-prov-o-20130430/}.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b91 ###bbsrt2
%b6 ###
\bibitem{isbn:9781315351148}
%
\begin{botherref}
\oauthor{\binits{B.}~\bsnm{Mons}},
Data Stewardship for Open Science,
1st edn,
Taylor \& Francis,
p.~240.
ISBN \bisbn{9781315351148}.
\end{botherref}
%
\OrigBibText
B.~Mons,
\textit{Data Stewardship for Open Science},
1st edn,
Taylor \& Francis,
p.~240.
ISBN 9781315351148.
\endOrigBibText
\bptok{structpyb}
\endbibitem

>>>>

%b42 ###bbsrt2
%b30 ###
\bibitem{doi:10.17487/rfc3987}
%
\begin{botherref}
\oauthor{\binits{M.}~\bsnm{Duerst}} and
\oauthor{\binits{M.}~\bsnm{Suignard}},
Internationalized resource identifiers ({IRI}s),
RFC 3987,
Internet Requests for Comments,
RFC Editor,
\byear(2005).
\bid{doi={10.17487/rfc3987}}
\end{botherref}
%
\OrigBibText
M.~Duerst and
M.~Suignard,
Internationalized resource identifiers ({IRI}s),
RFC 3987,
2005.
doi:10.17487/rfc3987.
\url{https://www.rfc-editor.org/info/rfc3987}.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b74 ###bbsrt2
%b26 ###
\bibitem{doi:10.17487/rfc8493}
%
\begin{botherref}
\oauthor{\binits{J.}~\bsnm{Kunze}},
\oauthor{\binits{J.}~\bsnm{Littman}},
\oauthor{\binits{E.}~\bsnm{Madden}},
\oauthor{\binits{J.}~\bsnm{Scancella}} and
\oauthor{\binits{C.}~\bsnm{Adams}},
The {BagIt} File Packaging Format,
(V1.0), 
RFC 8493,
Internet Requests for Comments,
RFC Editor,
(\byear{2018}).
\bid{doi={10.17487/RFC8493}}
\end{botherref}
%
\OrigBibText
J.~Kunze,
J.~Littman,
E.~Madden,
J.~Scancella and
C.~Adams,
The {BagIt} File Packaging Format (V1.0),
Technical Report,
2018.
doi:10.17487/RFC8493.
\url{https://www.rfc-editor.org/info/rfc8493}.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b81 ###bbsrt2
%b102 ###
\bibitem{PROVO}
%
\begin{botherref}
\oauthor{\binits{T.}~\bsnm{Lebo}},
\oauthor{\binits{S.}~\bsnm{Sahoo}},
\oauthor{\binits{D.}~\bsnm{McGuinness}},
\oauthor{\binits{K.}~\bsnm{Belhajjame}},
\oauthor{\binits{J.}~\bsnm{Cheney}},
\oauthor{\binits{D.}~\bsnm{Corsar}},
\oauthor{\binits{D.}~\bsnm{Garijo}},
\oauthor{\binits{S.}~\bsnm{Soiland-Reyes}},
\oauthor{\binits{S.}~\bsnm{Zednik}} and
\oauthor{\binits{J.}~\bsnm{Zhao}},
PROV-O: The PROV Ontology,
W3C Recommendation 30 April \byear{2013}.
\url{http://www.w3.org/TR/2013/REC-prov-o-20130430/}.
\end{botherref}
%
\OrigBibText
T.~Lebo,
S.~Sahoo,
D.~McGuinness,
K.~Belhajjame,
J.~Cheney,
D.~Corsar,
D.~Garijo,
S.~Soiland-Reyes,
S.~Zednik and
J.~Zhao,
PROV-O: The PROV Ontology,
2013,
W3C Recommendation 30 April 2013.
\url{http://www.w3.org/TR/2013/REC-prov-o-20130430/}.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b91 ###bbsrt2
%b6 ###
\bibitem{isbn:9781315351148}
%
\begin{bbook}
\oauthor{\binits{B.}~\bsnm{Mons}},
\bbtitle{Data Stewardship for Open Science},
1st edn,
\bpublisher{Taylor \& Francis},
p.~240.
ISBN \bisbn{9781315351148}.
\end{bbook}
%
\OrigBibText
B.~Mons,
\textit{Data Stewardship for Open Science},
1st edn,
Taylor \& Francis,
p.~240.
ISBN 9781315351148.
\endOrigBibText
\bptok{structpyb}
\endbibitem
